Modelling writing hesitations in text writing as finite mixture process

### 2023-07-24 report/results.Rmd
Manuscript with appendices separately

```{r include = F}
library(tidyverse)
library(kableExtra)
library(janitor)
library(brms)
library(polspline)
library(patchwork)
library(rmdformats)
library(gridExtra)
library(grid)
library(gtable)
library(scales)
library(ggthemes)
source("../scripts/functions.R")
source("scripts/get_pdens_plot.R")

@@

run <- FALSE

if(run){
  file <- list.files("../stanout", pattern = "sims", full.names = T, recursive = T)
  ds <- str_remove_all(file, "\\.|\\/|stanout|all_sims.csv") %>% 
    str_to_upper() %>% 
    str_replace(., "PLANTRA", "PLanTra")
  ds <- ds[-6]
  plots <- list()
  plots <- map(1:length(ds), ~get_pdens_plot(file[.], max_iki = 2000, ds = ds[.])) 
  #plots <- map(1, ~get_pdens_plot(file[.], max_iki = 2000, ds = ds[.])) 
  plots_fin <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] +
    plot_layout(guides = "collect") &
  #  plot_annotation(tag_levels = 'A') & 
    theme(legend.position = 'bottom')
  saveRDS(plots_fin, "objects/fitplots.rda", compress = "xz")
}

readRDS("objects/fitplots.rda")
```

>>>>

```{r include = F}
library(tidyverse)
library(kableExtra)
library(janitor)
library(brms)
library(polspline)
library(patchwork)
library(rmdformats)
library(rmarkdown)
library(gridExtra)
library(grid)
library(knitr)
library(gtable)
library(scales)
library(ggthemes)
source("../scripts/functions.R")
source("scripts/get_pdens_plot.R")

@@

run <- FALSE
if(run){
  file <- list.files("../stanout", pattern = "sims", full.names = T, recursive = T)
  ds <- str_remove_all(file, "\\.|\\/|stanout|all_sims.csv") %>% 
    str_to_upper() %>% 
    str_replace(., "PLANTRA", "PLanTra")
  ds <- ds[-6]
  plots <- list()
  plots <- map(1:length(ds), ~get_pdens_plot(file[.], max_iki = 2000, ds = ds[.])) 
  #plots <- map(1, ~get_pdens_plot(file[.], max_iki = 2000, ds = ds[.])) 
  plots_fin <- plots[[1]] / plots[[2]] / plots[[3]] / plots[[4]] / plots[[5]] / plots[[6]] +
    plot_layout(guides = "collect") &
  #  plot_annotation(tag_levels = 'A') & 
    theme(legend.position = 'bottom')
  ggsave("objects/fitplots.pdf", plots_fin, height = 10, width = 6)
#  saveRDS(plots_fin, "objects/fitplots.rda", compress = "xz")
}

include_graphics("objects/fitplots.pdf")
```

\begin{figure}
\includegraphics{objects/fitplots.pdf}
\end{figure}
